---
output: github_document
---

# Assigning numerical values
```{r}
dur_hablo_stressed <-616.045
dur_hablo_unstressed <- 479.146
dur_o_stressed <-239.573
dur_o_unstressed <- 147.061
int_o_stressed <- 66.1266
int_o_unstressed <- 68.4125
f0_o_stressed <-196.5217
f0_o_unstressed <-308.5264
```

# Doing Calculations
```{r}
dur_hablo_unstressed - dur_hablo_stressed

dur_o_stressed-dur_o_unstressed

int_o_stressed-int_o_unstressed

f0_o_stressed-f0_o_unstressed

```

# Observations

I thought it was very interesting that the duration of the unstressed 'o', `r dur_o_unstressed`, was almost half of that of the stressed 'o', `r dur_o_stressed`. The intensity for the two o's seemed to be pretty similar (`r int_o_stressed` versus `r int_o_unstressed`).
Lasltly, the duration of the stressed 'hablo', `r dur_hablo_stressed`, was longer than that of the unstressed 'hablo', `r dur_hablo_unstressed`. This actually made me wonder if perhaps I produced the stressed word more carefully than the unstressed one. (But I re-recorded the sound and it was quite similar.)
